Title here

### 2020-07-16 analysis/paper/paper.tex
more results

@@

Figure\textasciitilde{}\ref{fig:asymsam-timeseries} shows the resulting
Asymmetric and Symmetric time series corresponding to 700 and 30hPa.
blablababla

@@

Correlations between the Asymmetric and Symmetric series are rather
constant throught the troposphere, fluctiating between 0.39 and 0.45
(Figure\textasciitilde{}\ref{fig:cor-lev}). Futhermore, the
cross-correlation of each series across levels --shown in
Figure\textasciitilde{}\ref{fig:cross-correlation}-- are high in the
trosposphere (greater than 0.9) for both indices. This suggests that
both the Asymmetric and the Symemtric component of the tropospheric SAM
are highly vertically coherent, both in their individual evolution and
their temporal relationship. This is to be expected since the SAM is
mostly equivalent barotropic (citaaaa).

In the stratosphere the situation is different. As can be seen in
Figure\textasciitilde{}\ref{fig:cor-lev}, the relationship between the
Asymmetric and Symmetric indices varies with height above 100 hPa. It
starts to decreese right over the tropopause, reaches a minium of 0.21
at 20 hPa and then it increases again monotonically with height up to
the uppermost level of the reanalysis. The cross-correlation across
levels in the stratosphere is generally weaker than in the troposphere
(Figure\textasciitilde{}\ref{fig:cross-correlation}). Furthermore, above
100 hPa, the cross-correlation decreases more rapdily with height for
the Symmetric SAM than for the Asymmetric SAM as evidenced by the wider
dark red areas near the diagonal in
Figure\textasciitilde{}\ref{fig:cross-correlation}b)
vs.~Figure\textasciitilde{}\ref{fig:cross-correlation}c). Moreover, the
stratospheric Symmetric SAM seems to be slightly more connected to the
trosposphere than the Asymmetric SAM; this can be seen by the lower
correlation values in the top right quadrant of
Figure\textasciitilde{}\ref{fig:cross-correlation}b) in comparison with
Figure\textasciitilde{}\ref{fig:cross-correlation}c).

@@

Figure\textasciitilde{}\ref{fig:cross-correlation}a) show the
cross-correlation across levels for the Full SAM index. \ldots{}..

@@

Figure\textasciitilde{}\ref{fig:2d-regr} shows the spatial year-long
regression for selected levels. In the troposphere the Full annular mode
is clearly ``contaminated'' with well known zonal asymemtries (panels g
and j) which are succesfully sepparated by our methodology (panels h, i,
k and l). In the stratosphere, the spatial pattern associated with the
Full SAM is much more clearly dominated by a zonally symmetric,
monopolar structure (panels a and d) that is, however, not perfectly
centered in the south pole. The monopoloe obtained by multiple
regression with the Asymmetric and Symmetric SAM (panels c and f in
Figure\textasciitilde{}\ref{fig:2d-regr}) is much more symmetric and the
shift from total symmetry is captured by the regression pattern of the
Asymmetric SAM as a wave-1 pattern (panels b and e).

\begin{figure}
\includegraphics{vertical-regression-1} \caption[Asymmetric coefficient of the multiple regression of mean monthly geopotential height anomalies between 65 and 40 South]{Asymmetric coefficient of the multiple regression of mean monthly geopotential height anomalies between 65 and 40 South. Values are standarised by the standard deviation at each level. (this caption needs some love)}\label{fig:vertical-regression}
\end{figure}

@@

\begin{figure}
\includegraphics{wave-amplitude-700-1} \caption[Planteray wave amplitude for the regression patterns at 700 hPa]{Planteray wave amplitude for the regression patterns at 700 hPa.}\label{fig:wave-amplitude-700}
\end{figure}

@@

\begin{figure}
\includegraphics{wave-amplitude-30-1} \caption[Planteray wave amplitude for the regression patterns at 30 hPa]{Planteray wave amplitude for the regression patterns at 30 hPa.}\label{fig:wave-amplitude-30}
\end{figure}

@@

>>>>

\subsection{Temporal evolution}

@@

Figure \ref{fig:asymsam-timeseries} shows the resulting Asymmetric and
Symmetric time series corresponding to 700 and 30hPa. blablababla

@@

Correlations between the Asymmetric and Symmetric series are rather
constant throught the troposphere, fluctiating between 0.39 and 0.45
(Figure \ref{fig:cor-lev}). Futhermore, the cross-correlation of each
series across levels --shown in Figure \ref{fig:cross-correlation}-- are
high in the trosposphere (greater than 0.9) for both indices. This
suggests that both the Asymmetric and the Symemtric component of the
tropospheric SAM are highly vertically coherent, both in their
individual evolution and their temporal relationship. This is to be
expected since the SAM is mostly equivalent barotropic (citaaaa).

In the stratosphere the situation is different. As can be seen in Figure
\ref{fig:cor-lev}, the relationship between the Asymmetric and Symmetric
indices varies with height above 100 hPa. It starts to decreese right
over the tropopause, reaches a minium of 0.21 at 20 hPa and then it
increases again monotonically with height up to the uppermost level of
the reanalysis. The cross-correlation across levels in the stratosphere
is generally weaker than in the troposphere (Figure
\ref{fig:cross-correlation}). Furthermore, above 100 hPa, the
cross-correlation decreases more rapdily with height for the Symmetric
SAM than for the Asymmetric SAM as evidenced by the wider dark red areas
near the diagonal in Figure \ref{fig:cross-correlation}b) vs.~Figure
\ref{fig:cross-correlation}c). Moreover, the stratospheric Symmetric SAM
seems to be slightly more connected to the trosposphere than the
Asymmetric SAM; this can be seen by the lower correlation values in the
top right quadrant of Figure \ref{fig:cross-correlation}b) in comparison
with Figure \ref{fig:cross-correlation}c).

@@

Figure \ref{fig:cross-correlation}a) show the cross-correlation across
levels for the Full SAM index. \ldots{}..

\subsection{Spatial patterns}

@@

Figure \ref{fig:2d-regr} shows the spatial year-long regression for
selected levels. In the troposphere the Full annular mode is clearly
``contaminated'' with well known zonal asymemtries (panels g and j)
which are succesfully sepparated by our methodology (panels h, i, k and
l). In the stratosphere, the spatial pattern associated with the Full
SAM is much more clearly dominated by a zonally symmetric, monopolar
structure (panels a and d) that is, however, not perfectly centered in
the south pole. The monopoloe obtained by multiple regression with the
Asymmetric and Symmetric SAM (panels c and f in Figure
\ref{fig:2d-regr}) is much more symmetric and the shift from total
symmetry is captured by the regression pattern of the Asymmetric SAM as
a wave-1 pattern (panels b and e).

\begin{figure}
\includegraphics{wave-amplitude-1} \caption[Planteray wave amplitude for the regression patterns at 50 and 700 hPa]{Planteray wave amplitude for the regression patterns at 50 and 700 hPa.}\label{fig:wave-amplitude}
\end{figure}

The amplitude of each zonal wave number at each latitude at 50 hPa and
700 hPa is shown in Figure \ref{fig:wave-amplitude}, where wave number
zero represents the zonal mean. Comparing between rows, this Figure
quantifies the relatively clean separation between the zonally symmetric
and zonally asymmetric structures, as its evident how the mixture of
waves of the Full field (first row) is very similar to the sum of the
waves of the Asymmetric and Symmetric field (second and third row,
respectively). The second row of Figure \ref{fig:wave-amplitude} shows
that the Asymmetric SAM is overwhelmingly dominated by wave 1 in the
stratosphere (panel b), while in the stratosphere it is composed of
zonal waves 3 to 1 in decreasing level of importance.

\begin{figure}
\includegraphics{vertical-regression-1} \caption[Asymmetric coefficient of the multiple regression of mean monthly geopotential height anomalies between 65 and 40 South]{Asymmetric coefficient of the multiple regression of mean monthly geopotential height anomalies between 65 and 40 South. (this caption needs some love)}\label{fig:vertical-regression}
\end{figure}

From Figure \ref{fig:2d-regr} it appears that the vertical structure of
the Asymmetric SAM is equivalent barotropic in the troposphere but
baroclinic in the stratosphere. Anomalies are centerd in the same
locations in the troposphere (panels h and k), but show westerly
displacement in the stratosphere (panesl b and e). This is expanded in
Figure \ref{fig:vertical-regression}, which shows a vertical crossection
of the regression coefficient corresponding to the middle row of Figure
\ref{fig:2d-regr}, area-weighted averaged between 65 and 40 degrees
South. Below 100 hPa, anomalies are completely vertical, while above
they show an important westerly tilt with height.

@@

@@

\subsubsection{Impacts}

@@

\begin{figure}
\includegraphics{A7-1} \caption[ ]{ }\label{fig:A7}
\end{figure}
